Cultural Transmission and the Social Contexts of Technological Transitions during the Late Paleolithic of Korea

### 2023-04-11 analysis/paper/paper.qmd
add one para to address Fitzhugh's feedbacks

>>>>

We concede that our work is rather speculative and provides only a limited explanation of the social contexts surrounding the spread of stemmed points. Although social learning and migration or drift models requires approximate estimates for population and generation turnover required to transmit knowledge of new technology, we were unable to employ this approach due to the large number of assumptions required to cover a 25,000-year time span. In her simulation study, Garvey was able to derive the population at a particular site based on the number of rooms [@garvey2018current], but our research sites lacked sufficient information to utilize this method. Moreover, we recognize that we did not account for the possibility of the shape of stone artifacts being modified through reuse and resharpening, which can result in the remaining shape of stemmed points being different from their original form through inherited technology (i.e. the Frison Effect) [@dibble1995middle; @jelinek1976form; @frison1968functional]. Furthermore, we only considered two types of biases, as our primary goal was to understand the general trajectory of technological transition, and we had limited empirical evidence to explore a multiplicity of conjectural scenarios. In future research, we plan to focus more closely on individual assemblages and site occupation to gain a better understanding of the population responsible for creating and using stemmed points. By so doing, we anticipate achieving a more exhaustive understanding of the morphology of stemmed points and the mechanisms behind their transmission.
